---
title: "Logistic Regression with a Small Sample"
cache: true
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, load the `weisiger2014` data set.

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)

# load weisiger2014 data
weis <- crdata::weisiger2014

# show weisiger2014 data set
glimpse(weis)
```

To facilitate interpretation and comparability, rescale the explanatory variables using `arm::rescale()` (i.e., so that continuous explanatory variables have mean zero and SD 0.5 and the binary explanatory variables to have mean zero.)

```{r, "Show data"}
# rescale weisiger2014 explanatory variables using arm::rescale()
rs_weis <- weis %>%
  mutate(across(polity_conq:coord, arm::rescale)) %>%
  glimpse()
```

Now we fit three models.

1. Least squares, which replicates Model 3 of Table 2 of Weisiger (2014).
1. A logit alternative, fit with maximum likelihood.
1. A logit alternative, fit with penalized maximum likelihood using the {brglm2} package.

```{r "Fit models"}
# fit models 
f <- resist ~ polity_conq + lndist + terrain + soldperterr + gdppc2 + coord
ls <- lm(f, data = rs_weis) # lpm (replicates Table 2 Model 3 of Weisiger 2014)
mle <- glm(f, data = rs_weis, family = "binomial") # logistic regression
pmle <- glm(f, data = rs_weis, family = "binomial", method = brglm2::brglmFit) # logistic regression
```

To interpret the results, we might focus on Weisiger's Hypothesis 12.

> **Hypothesis:** Resistance will be more likely when the pre-war political leader remains at large in the conquered country.

The table below compares the estimates. 

```{r "Print tables"}
modelsummary::modelsummary(list("Least Squares" = ls, 
                                "Logit via MLE" = mle, 
                                "Logit via PMLE" = pmle))
```

The plot below compares the estimates. Notice that Firth's PML estimator produces smaller estimates and CIs.

```{r "Plot PML and ML"}
modelsummary::modelplot(list("Logit via MLE" = mle, "Logit via PMLE" = pmle), conf_level = 0.90)
```
